Use package

### 2015-10-31 020-lsh-with-package.Rmd
Redo the LSH with new sections and smarter minhashes/bands

```{r}
library("textreuse")
library("dplyr")
options("mc.cores" = 6L)
```

@@

```{r}
cache_corpus <- "cache/corpus-sections-minash-n1500-seed623.rda"
if (!file.exists(cache_corpus)) {
  message("Creating the corpus")
  minhash <- minhash_generator(n = 1500, seed = 623)
  sections <- TextReuseCorpus(dir = "legal-codes-split/",
                              tokenizer = tokenize_ngrams, n = 5,
                              keep_tokens = FALSE,
                              minhash_func = minhash)
  save(sections, minhash, file = cache_corpus)
} else {
  message("Loading corpus from cache")
  load(file = cache_corpus)
}
```

@@

```{r}
cache_lsh <- "cache/lsh-sections.rda"
if (!file.exists(cache_lsh)) {
  message("Running LSH analysis")
  section_buckets <- lsh(sections, bands = 500)
  section_candidates <- lsh_candidates(section_buckets)
  section_scores <- lsh_compare(section_candidates, sections, jaccard_similarity)
  save(section_buckets, section_candidates, section_scores, file = cache_lsh)
  saveRDS(section_scores, "cache/section-scores.rds")
} else {
  message("Loading LSH objects from cache")
  load(file = cache_lsh)
}
```

>>>>

```{r message=FALSE}
library("textreuse")
library("dplyr")
options("mc.cores" = 6L)
```

We want to have the smallest number of hashes and bands while still detecting all reasonable matchs. We will set the bands and number of minhashes as follows.

```{r}
h <- 120
b <- 60
lsh_threshold(h, b)
```

@@

```{r}
cache_corpus <- "cache/corpus-sections-minash-n120-seed623.rda"
if (!file.exists(cache_corpus)) {
  message("Creating the corpus.")
  minhash <- minhash_generator(n = h, seed = 623)
  sections <- TextReuseCorpus(dir = "legal-codes-split/",
                              tokenizer = tokenize_ngrams, n = 5,
                              keep_tokens = FALSE,
                              minhash_func = minhash)
  save(sections, minhash, file = cache_corpus)
} else {
  message("Loading corpus from cache.")
  load(file = cache_corpus)
}
```

@@

```{r}
cache_lsh <- "cache/lsh-sections.rda"
if (!file.exists(cache_lsh)) {
  message("Running LSH analysis.")
  section_buckets <- lsh(sections, bands = b)
  section_candidates <- lsh_candidates(section_buckets)
  section_scores <- lsh_compare(section_candidates, sections, jaccard_similarity)
  save(section_buckets, section_candidates, section_scores, file = cache_lsh)
  saveRDS(section_scores, "cache/section-scores.rds")
} else {
  message("Loading LSH objects from cache.")
  load(file = cache_lsh)
}
```
